### 2023-10-20 README.Rmd
updated tests and formatted function - 231020

Now imagine you included a validation/ holdout task with three
alternatives as well as an no-buy option. We specify the <code>data</code> argument and the column index of <code>id</code>. Since we also have a *no-buy* alternative in our validation task, we next specify the <code>None</code> argument, otherwise we would have left it empty. Afterwards, we specify the number of products (<code>prod</code>) we include (excluding the *no-buy* alternative), which we define in the next step with the argument <code>prod.levels</code>. If we look back at the data frame, we can see that the first alternative in the holdout task <code>c(4, 9, 19)</code> is composed of the following attribute levels <code>Att1_Lev1</code>, <code>Att2_Lev1</code>, and <code>Att3_Lev5</code>.

@@

```{r}
HOT <- createHOT(
  data = CBC, # data frame
  id = 1, # column index of the id
  None = 21, # column index of none alternative
  prod = 3, # number of alternatives in validation task (excluding none)
  prod.levels = list(c(4, 9, 19), c(8, 12, 17), c(5, 10, 17)), # column index of the attribute levels for each alternative
  coding = c(0, 0, 0), # how the attributes were coded
  method = "CBC", # method
  choice = 22 # column index of choice
)
```

@@

Again, we first define <code>data</code>. The <code>id</code> is saved in the first column. The utilities for the <code>None</code> parameter are stored in the 15th column, and we again set <code>prod</code> to 3 (**excluding** the *no-buy* alternative). Next, we define the <code>prod.levels</code> for each alternative. For example, we can see that the second see that the second alternative is composed of <code>Att1_Lev5</code>, <code>Att2_Lev4</code>, and <code>60</code> which is the value that should be interpolated. We can see that this value is the one that needs to be interpolated if we take a closer look at the <code>coding</code> argument. This tells us that the first two attributes (<code>Att1_Lev5</code>, <code>Att2_Lev4</code> in the case of alternative 2) are part-worth coded (<code>0</code>) while the third attribute is linear coded (<code>1</code>).

@@

```{r}
CBC <- createHOT(
  data = CBC_lin, # data frame
  id = 1, # column index of the id
  None = 15, # column index of none alternative
  prod = 3, # number of alternatives in validation task (excluding none)
  prod.levels = list(c(4, 9, 60), c(8, 12, 40), c(5, 10, 45)), # column index of the attribute levels for each alternative (for linear coded we specify value to be interpolated)
  interpolate.levels = list(c(10, 20, 30, 40, 50, 60, 70)), # actual values for the levels that should be interpolated
  lin.p = 14, # column index of the linear coded variable
  coding = c(0, 0, 1), # coding of the 3 attributes; 0 = part-worth, 1 = linear, 2 = piecewise
  method = "CBC", # method
  varskeep = 17, # column index of variables that should be kept in the dataframe
  choice = 16 # column index of choice
)
```

>>>>

Now imagine you included a validation/ holdout task with three
alternatives as well as an no-buy option. We specify the <code>data</code> argument and the column index of <code>id</code>. Since we also have a *no-buy* alternative in our validation task, we next specify the <code>none</code> argument, otherwise we would have left it empty. Afterwards, we specify the number of products (<code>prod</code>) we include (excluding the *no-buy* alternative), which we define in the next step with the argument <code>prod.levels</code>. If we look back at the data frame, we can see that the first alternative in the holdout task <code>c(4, 9, 19)</code> is composed of the following attribute levels <code>Att1_Lev1</code>, <code>Att2_Lev1</code>, and <code>Att3_Lev5</code>.

@@

```{r}
HOT <- createHOT(
  data = CBC, # data frame
  id = 1, # column index of the id
  none = 21, # column index of none alternative
  prod = 3, # number of alternatives in validation task (excluding none)
  prod.levels = list(c(4, 9, 19), c(8, 12, 17), c(5, 10, 17)), # column index of the attribute levels for each alternative
  coding = c(0, 0, 0), # how the attributes were coded
  method = "CBC", # method
  choice = 22 # column index of choice
)
```

@@

Again, we first define <code>data</code>. The <code>id</code> is saved in the first column. The utilities for the <code>none</code> parameter are stored in the 15th column, and we again set <code>prod</code> to 3 (**excluding** the *no-buy* alternative). Next, we define the <code>prod.levels</code> for each alternative. For example, we can see that the second see that the second alternative is composed of <code>Att1_Lev5</code>, <code>Att2_Lev4</code>, and <code>60</code> which is the value that should be interpolated. We can see that this value is the one that needs to be interpolated if we take a closer look at the <code>coding</code> argument. This tells us that the first two attributes (<code>Att1_Lev5</code>, <code>Att2_Lev4</code> in the case of alternative 2) are part-worth coded (<code>0</code>) while the third attribute is linear coded (<code>1</code>).

@@

```{r}
CBC <- createHOT(
  data = CBC_lin, # data frame
  id = 1, # column index of the id
  none = 15, # column index of none alternative
  prod = 3, # number of alternatives in validation task (excluding none)
  prod.levels = list(c(4, 9, 60), c(8, 12, 40), c(5, 10, 45)), # column index of the attribute levels for each alternative (for linear coded we specify value to be interpolated)
  interpolate.levels = list(c(10, 20, 30, 40, 50, 60, 70)), # actual values for the levels that should be interpolated
  lin.p = 14, # column index of the linear coded variable
  coding = c(0, 0, 1), # coding of the 3 attributes; 0 = part-worth, 1 = linear, 2 = piecewise
  method = "CBC", # method
  varskeep = 17, # column index of variables that should be kept in the dataframe
  choice = 16 # column index of choice
)
```
